---
title: "Visualization_ partI"
output: github_document
date: 10/02/2020
---

```{r setup}
library(tidyverse)
library(ggridges)
library(hexbin)
```

# Load the Weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```

## Scatterplots

Create my first scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

other approach

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Save and edit plot object

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```

## Advanced scatterplot

Start with the same one and make it fancy

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

What about the `aes` placement ?

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name)) + 
  geom_smooth(se = FALSE) # compare to the previous one!
```

Let's facet some things

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point() + 
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name) # check (name ~ .)

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, alpha = tmin, color = name)) + 
  geom_point() +  # different than putting the alpha = .5 here - check below
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)

weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .2) +
  geom_smooth(se = FALSE) + 
  facet_grid(. ~ name)
```

Let's combine some elements and try a new plot

```{r}
weather_df %>% 
    ggplot(aes(x = date, y = tmax, color = name))+
    geom_point(aes(size = prcp), alpha = .5) + 
    geom_smooth(se = FALSE) + 
    facet_grid (. ~ name)
```

## Some small notes

How many geoms have to exist?

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_smooth(se = FALSE)
```

You can use a neat geom!

```{r}
weather_df %>% 
  ggplot (aes(x = tmin, y = tmax)) +
  geom_bin2d()

weather_df %>% 
  ggplot (aes(x = tmin, y = tmax)) +
  geom_hex()

weather_df %>% 
  ggplot (aes(x = tmin, y = tmax)) +
  geom_density2d() + 
  geom_point(alpha = .3)
```

## Univariate plots

histograms are really great.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin)) + 
  geom_histogram()
```

can we add color...

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_histogram(position = "dodge")

weather_df %>% 
  ggplot(aes(x = tmin)) + 
  geom_histogram() +
  facet_grid(. ~ name)
```

Let's try a new geometry

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_density(alpha = .3) #check adjust = x
```

what about boxplots

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin)) + 
  geom_boxplot()
```

Trendy plots

```{r}
weather_df %>% 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin(alpha = .5) + 
  stat_summary(fun = "median")
```

Ridge plots -- the most popular plot of 2017

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = name)) +
  geom_density_ridges()
```


## Save and embed

Save a scatterplot

```{r}
weather_plot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5)

ggsave("./results/weather_plot.pdf", weather_plot, width = 8, height = 5)
```

# what about embeding...

```{r, fig.width=6, fig.height=3}
weather_plot
```

embed at different size

```{r, fig.width=12, fig.height=6}
weather_plot
```