---
title: "Visualization_ partII"
output: github_document
date: 10/02/2020
---

```{r setup}
library(tidyverse)
library(patchwork)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```

## remember this plot

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5)
```

## labels

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  labs(
    title = "Tempaerature Plot",
    x = "Minimum daily Temperature (ºC)",
    y = "Maximum daily Temperature (ºC)",
      caption = "Data from rnoaa package; temperatures in 2017"
  )
```

## scales

Start with the same plot

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  labs(
    title = "Tempaerature Plot",
    x = "Minimum daily Temperature (ºC)",
    y = "Maximum daily Temperature (ºC)",
      caption = "Data from rnoaa package; temperatures in 2017"
  ) + 
  scale_x_continuous(
    breaks = c(-15, 0, 15),
    labels = c("-15ºC", "0", "15")
  ) +
  scale_y_continuous(
    trans = "log",  #sqrt could be an option
    position = "right"
  )
```

Lets look at color scales

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  labs(
    title = "Tempaerature Plot",
    x = "Minimum daily Temperature (ºC)",
    y = "Maximum daily Temperature (ºC)",
      caption = "Data from rnoaa package; temperatures in 2017"
  ) +
  scale_color_hue(
    name = "Location",
    h = c(100, 300)
  )
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  labs(
    title = "Tempaerature Plot",
    x = "Minimum daily Temperature (ºC)",
    y = "Maximum daily Temperature (ºC)",
      caption = "Data from rnoaa package; temperatures in 2017"
  ) +
  viridis::scale_color_viridis( #good for colorblind people AND is better gray scale print than default
    name = "Location",
    discrete = TRUE
  )
```

## themes

shift the legend

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  labs(
    title = "Tempaerature Plot",
    x = "Minimum daily Temperature (ºC)",
    y = "Maximum daily Temperature (ºC)",
      caption = "Data from rnoaa package; temperatures in 2017"
  ) +
  viridis::scale_color_viridis( #good for colorblind people AND is better gray scale print than default
    name = "Location",
    discrete = TRUE
  ) +
  theme(legend.position = "bottom")
```


change the overall theme

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  labs(
    title = "Tempaerature Plot",
    x = "Minimum daily Temperature (ºC)",
    y = "Maximum daily Temperature (ºC)",
      caption = "Data from rnoaa package; temperatures in 2017"
  ) +
  viridis::scale_color_viridis(  #good for colorblind people AND is better gray scale print than default
    name = "Location",
    discrete = TRUE
  ) + 
  theme_minimal()
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  labs(
    title = "Tempaerature Plot",
    x = "Minimum daily Temperature (ºC)",
    y = "Maximum daily Temperature (ºC)",
      caption = "Data from rnoaa package; temperatures in 2017"
  ) +
  viridis::scale_color_viridis(  #good for colorblind people AND is better gray scale print than default
    name = "Location",
    discrete = TRUE
  ) + 
  ggthemes::theme_economist() +
  theme(legend.position = "bottom") ## be careful because once you use a theme is overrides all theme elements before
```

## setting options
Put this in the begginign to set as default option througout the rmkd file

```{r, eval = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Data args in `geom`

```{r}
central_park = 
  weather_df %>% 
  filter(name == "CentralPark_NY")

waikiki = 
  weather_df %>% 
  filter(name == "Waikiki_HA")

ggplot(data = waikiki, aes(x = date, y = tmax, color = name))+
  geom_point() + 
  geom_line(data = central_park)
```


## `patchwork`

remeber faceting?
```{r}
weather_df %>% 
  ggplot(aes(x = tmin, fill = name)) + 
  geom_density(alpha = .5) +
  facet_grid(. ~ name)
```

what happens when you want multipanel plot but cant facet?

```{r}
tmax_tmin_p = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = .5) +
  theme(legend.position = "none")

prcp_dens_p = 
  weather_df %>% 
  filter(prcp > 0) %>% 
  ggplot(aes(x = prcp, fill = name)) + 
  geom_density(alpha = .5) +
  theme(legend.position = "none")

tmax_date_p = 
  weather_df %>% 
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point() +
  geom_smooth(se = FALSE) +
  theme(legend.position = "none")

tmax_tmin_p + prcp_dens_p + tmax_date_p
tmax_tmin_p / (prcp_dens_p + tmax_date_p)
tmax_tmin_p + (prcp_dens_p + tmax_date_p)
(tmax_tmin_p + prcp_dens_p) / tmax_date_p

```

## Data manipulation

Control your factors.
```{r}
weather_df %>%
  mutate(
    name = factor(name),
    name = forcats::fct_relevel(name, c("Waikiki_HA")) # we will see that you can relevel by stats!
  ) %>% 
  ggplot(aes(y = tmax, x = name, fill = name)) + 
  geom_violin(alpha = .5)
```

What if I wanted densities for tmin and tmax simultaneously?

```{r}
weather_df %>%
  filter(name == "CentralPark_NY") %>% 
  pivot_longer(
    tmax:tmin,
    names_to = "observation",
    values_to = "temperatures"
  ) %>% 
  ggplot(aes(x = temperatures, fill = observation)) + 
  geom_density(alpha = .5)

weather_df %>%
  pivot_longer(
    tmax:tmin,
    names_to = "observation",
    values_to = "temperatures"
  ) %>% 
  ggplot(aes(x = temperatures, fill = observation)) + 
  geom_density(alpha = .5) +
  facet_grid(. ~ name)
```


